---
title: "Summarizing Users and Friends Data"
author: "ES"
date: "August 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Installing packages, setting directory

```{r, echo=FALSE}
rm(list=ls())

library(jsonlite)
library(magrittr)
library(knitr)
library(ggplot2)

setwd("C:/Users/SV Tech Holdings/Documents/NYU MSBA/Capstone/Data/User_Data")

```

#### Reading the Yelp - User JSON file

```{r users, echo=FALSE,eval=FALSE}
# read in individual JSON lines
json_file <- "yelp_academic_dataset_user.json"

# turn it into a proper array by separating each object with a "," and
# wrapping that up in an array with "[]"'s.

data_user <- fromJSON(sprintf("[%s]", paste(readLines(json_file), collapse=","))) # flattening and reading into dataframe, takes a long time

# Saving file as a Rdata file
save(data_user,file="user_data.Rdata")

```

#### Extracting friends list and saving as RDS file for future retrieval

```{r echo=FALSE,eval=FALSE}
# Save the friends list as a separate object
friends_list=data_user$friends
names(friends_list)=data_user$user_id # assigning user_ids to each vector in list

#Saving friends list in a easy to retrieve R object 
saveRDS(friends_list,"friends_list.rds") # save list for retrieval later with readRDS()
#save(friends_list,file="Friends_List.Rdata")

# Cleaning environment
rm(list=ls())
```

#### Reading RDS file and converting to list

```{r echo=FALSE}
friends_list=as.matrix(readRDS("friends_list.rds"))

# Converting to data frame and counting no of friends per user IDs
user_friends=data.frame(rownames(friends_list)) %>% setNames("UserIDs")
user_friends$No_of_Friends=do.call(rbind,lapply(friends_list[,1],function(x) length(x)))
user_friends$Friends_IDs=friends_list[,1]

#write.csv(as.matrix(user_friends),"user_friends.csv")

# Summary 
min_f = min(user_friends$No_of_Friends) %>% round(digits=0)
max_f = max(user_friends$No_of_Friends) %>% round(digits=0)
mean_f = mean(user_friends$No_of_Friends) %>% round(digits=0)
unique_users=length(unique(user_friends$UserIDs))

user_summary = c(min_f,mean_f,max_f) %>% t() %>% data.frame()

# Fraction of users with social edge
friend_freq=as.data.frame(table(user_friends$No_of_Friends)) %>% setNames(c("Number of Friends","Number of Users"))
plot(friend_freq,main="Distribution of number of users to friends")
tusers=sum(friend_freq$`Number of Users`)
friend_freq$Percent_of_Users=round((friend_freq$`Number of Users`/sum(friend_freq$`Number of Users`))*100,2)

```

# Summary of users and their social edges

```{r,echo=FALSE}
user_summary %>% kable(col.names=c("Minimum","Average","Maximum"),format = "pandoc",caption = "Number of friends",align='c')

data.frame(friend_freq$Percent_of_Users,friend_freq$`Number of Friends`) %>% head(n=10) %>% kable(col.names=c("Percent of Users","Number of Friends"),format = "pandoc", caption = "Fraction of users with a social edge",align='c')

```

```{r}

friends_list2=lapply(friends_list, `length<-`, max(lengths(friends_list))) # running out of memory
a=unlist(friends_list,use.names = F,recursive = F)

library(plyr)
friends_list1=lapply(friends_list, as.data.frame,stringsAsFactors=FALSE) # running out of memory
mydf = rbind.fill(friends_list1)
#a=unlist(friends_list,use.names = F,recursive = T)

n=length(friends_list)
for(x in 1:n) {
b=data.frame(user_friends$Friends_IDs[[x]])
b$user=user_friends$UserIDs[[x]]
x=x+1
}